---
title: Community Science Contributions
weight: 3
knit: (function(input, ...) { source(here::here("R/knit_render.R"), local = TRUE)$value(input, ...) })
gridVisible: true
filtersVisible: true
obsTableVisible: true
regionField: "!statusAsRegion"
statusColors:
  confirmed: '#5a96d2'
  historical: '#decb90'
  new: '#7562b4'
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
options(error = rlang::entrace, rlang_backtrace_on_error = "full")
library(tidyverse)
plants <- read.csv("tabular_data/Saanich_Tracheophyta_incomplete-aligned-catalogue_2025-08-26-reduced-labels.csv")
plant.summary <- read.csv("tabular_data/Saanich_Tracheophyta_incomplete-aligned-catalogue_2025-08-26-prepared-taxa.csv", fileEncoding = "UTF-8") %>%
  filter(inSummary == 1)
new <- plant.summary %>% filter(str_detect(reportingStatus, "new")) 
confirmed <- plant.summary %>% filter(reportingStatus == 'confirmed') 
reported <- plant.summary %>% filter(reportingStatus == 'reported') 
# observed <- plant.summary %>% filter(iNatObservationStatus == 'observed')
```

## Community science contributions

Through the combined efforts of `r length(unique(plants$recordedBy))` individuals, the Saanich naturalist
community has now documented a total of `r nrow(plant.summary)` vascular plant species. Based on search
efforts over the last decade, `r round((nrow(confirmed)/(nrow(confirmed)+nrow(reported))*100), digits = 0)` percent
of the historically reported plant diversity has been confirmed and `r nrow(new)` new species reports added to the
list. Community members have now documented `r round((nrow(confirmed)/(nrow(plant.summary))*100), digits = 0)` percent
of the plant diversity known to the region on iNaturalist.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("scripts/Community_science_contributions_mapbox.R")
reportingStatusMap
```
